---
title: "Interactice Graph Examples"
author: "Joanne Pham"
date: "10/22/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) # If you want a global setting that doesn't show any code except for the plots, then just do echo = FALSE up here
```

Here, we will practice some interactive graphs and tables using built-in datasets and r packages.

- Interactive plots: {plotly}
- Interactive tables: {DT}

remember that if you want to select all of the files to commit, then just press Ctrl + A + space after clicking on just one line 

```{r, include= FALSE}
# Attach packages

library(tidyverse)
library(plotly)
library(DT)

```

### A. Interactive graph of iris dimensions

Using Edgar Anderson's famous 'iris' dataset

```{r, echo= FALSE}

iris_graph <- ggplot(data = iris, aes(x = Petal.Width, y = Petal.Length)) +
 geom_point(aes(size = Sepal.Width, 
                  color = Species), 
              alpha = 0.5) +
   theme_minimal() +
  labs(x = "Petal Width (cm)",
        y = "Petal Length (cm)",
        title = "My iris graph")
iris_graph

# to put an entire code chunk as comment, highlight and then press Cntrl + Shift + C

# if you want r to stop evaluating, then put echo=FALSE and then eval = False

ggplotly(iris_graph)
```

### Make an interactive table with DT

```{r}
datatable(msleep)
```

